Title

### 2023-06-12 main.tex
(\ /) (O.o) (> <) Bunny approves these changes.

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
{\color{red}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$}
 \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
con $p$ no está clara del lado derecho.}

\tbnote{Va, algo así (quitar lo 
rojo, dejar lo morado):}

{\color{purple} where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.}

\cpnote{
 Quizpa si se escribe $s(p)$ en vez de 
$s$ es mejor, pero piensale tambien . } 
\tbnote{Es cierto, mejor, ya lo puse}.\\

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
thi curve of states is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
\tbnote{Va, listo.}

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

\item \textbf{Bit flip map:} 
\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar} \tbnote{Va, puse explícitamente lo de que sólo se usa un qubit más abajo} \tbnote{Tambien puse la cita del trabajo brasileño}
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
\end{align*}
with $\sin s= \sqrt{p}$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
acuerdo igual cambia los siguientes} \tbnote{Va, ya los cambié}.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
{\color{purple} Note that in this case we actually only need one ancilla qubit
since the state $|\beta(p)\rangle$ is only two dimensional.}

The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.
{\color{purple}
For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
using an optical arrangement, and  it was indeed done 
by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).}

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

{\color{purple} However, since a Pauli dynamical map should begin at the
identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
$\theta$ an arbitrary real number. 
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.}
\end{itemize}

@@

{\color{red}
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
estos dos parrafos para que tengan un flujo mas chido. }
\tbnote{Va, lo cambié y agregué esto al paso 3. Propongo quitar lo rojo y dejar lo morado}
To fulfill this additional condition,  we restrict the first row of
$V$ writen as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last step is because the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
}

% }}}

\section{Conclusion} % {{{
\tbnote{Primera versión para ir teniendo algo escrito }\\

In this study, we focused on the analysis of Pauli channels in N-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.
% }}}

>>>>

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation\cpnote{no entiendo esta frase}. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
this curve of states is \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.}
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. }
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
\end{align*}
with $\sin s= \sqrt{p}$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
Note that in this case we actually only need one ancilla qubit
since the state $|\beta(p)\rangle$ is only two dimensional.

The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.
For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
using an optical arrangement, and  it was indeed done 
by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

However, since a Pauli dynamical map should begin at the
identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
$\theta$ an arbitrary real number. 
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\end{itemize}

@@

% }}}
\section{Conclusion} % {{{
\tbnote{Primera versión para ir teniendo algo escrito }\\

In this study, we focused on the analysis of Pauli channels in $N$-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.

\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
muy buena primera iteracion para las conclusiones!!! }
% }}}
